Figures from: Vertebrate host availability and the thermal properties of mosquito-borne parasite transmission

### 2023-06-16 manuscript-figures.Rmd
Update manuscript-figures.Rmd

# Label functions:
appender_sigmaH <- function(string) {
  unname(TeX(paste("$\\sigma_H = $", string)))
}
appender_KH <- function(string) {
  unname(TeX(paste("$K_H = $", string)))
}

@@

## PLOT ##
R0_plot <- R0_df %>%
  ggplot(mapping = aes(x = sigmaH_proxy, y = Temperature)) +
  # Mosquito thermal tolerance range lines
  geom_hline(
    data = MosqThermRange_df,
    aes(yintercept = CTmin_V0, colour = "VTTR"),
    lwd = 1.275
  ) +
  geom_hline(
    data = MosqThermRange_df,
    aes(yintercept = CTmax_V0, colour = "VTTR"),
    lwd = 1.275
  ) +
  # R0 contours for FINITE sigmaH:
  geom_contour_filled(
    data = filter(R0_df, sigmaH_proxy < infinite_divide**0.98),
    mapping = aes(z = R0),
    breaks = fill_breaks
  ) +
  # R0 contours for INFINITE sigmaH:
  geom_contour_filled(
    data = filter(R0_df, sigmaH_proxy > infinite_divide**1.02),
    mapping = aes(z = R0),
    breaks = fill_breaks
  ) +
  # R0 = 1 contour:
  geom_contour(aes(colour = "R0=1", z = R0), breaks = c(1), size = 1) +
  # Topt curve:
  geom_path(
    data = filter(Topt_for_R0_df, KH %in% c(.1, 1, 10)) %>% arrange(sigmaH_proxy),
    mapping = aes(
      x = sigmaH_proxy,
      y = median,
      colour = "Topt"
    ),
    lwd = 1,
    linetype = 1
  ) +
  # white lines breaking up finite/infinite sigmaH values
  geom_vline(
    aes(xintercept = 0.85 * infinite_divide),
    colour = "white",
    lwd = .8,
    show.legend = FALSE
  ) +
  geom_vline(
    aes(xintercept = infinite_divide),
    colour = "white",
    lwd = .8,
    show.legend = FALSE
  ) +
  geom_vline(
    aes(xintercept = 1.2 * infinite_divide),
    colour = "white",
    lwd = .8,
    show.legend = FALSE
  ) +
  # x-axis:
  scale_x_log10(
    name = TeX("Vertebrate host biting tolerance (bites per host per day)"),
    breaks = sigmaH_breaks_heatmap,
    labels = sigmaH_labels_heatmap,
    expand = c(0, 0)
  ) +
  # y-axis:
  scale_y_continuous(
    name = expression("Temperature "(degree * C)),
    expand = c(0, 0),
    limits = c(16, 35),
    breaks = seq(10, 36, by = 2)
  ) +
  # color:
  scale_colour_manual(
    name = "",
    labels = c(
      "R0=1" = unname(TeX("$R_0=1$")),
      "Topt" = "Transmission\nthermal\noptimum",
      "VTTR" = "Mosquito\nthermal\ntolerance\nlimit"
    ),
    values = c("black", "purple", "grey"),
    guide = guide_legend(
      order = 1,
      keyheight = unit(2, "cm"),
      override.aes = list(size = 6)
    )
  ) +
  # fill:
  scale_fill_manual(
    name = TeX("$R_0$"),
    values = my.cols,
    guide = guide_colorsteps(
      order = 2,
      breaks = fill_breaks,
      barheight = unit(8, "cm")
    )
  ) +
  # faceting:
  facet_grid(
    rows = vars(KH),
    cols = vars(system_label),
    labeller = labeller(.rows = mylabels,
                        .cols = R0_heatmap_labels),
    # repeat.tick.labels = "left"
  ) +
  # theme options:
  theme_minimal_hgrid(11) +
  theme(
    axis.line = element_line(),
    legend.text = element_text(size = 10),
    legend.text.align = 0,
    strip.text.y = ggtext::element_markdown(
      size = 7,
      hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 7,
      hjust = 0),
    panel.spacing = unit(2, "pt")
    )

@@

CTRange_plots <- CTRange_df %>%
  ## Set up plot ##
  # x-axis = population density, y-axis = temperature,
  # color = thermal extrema, linetype = sigmaH
  ggplot(
    aes(x = KH, y = value, linetype = as.factor(sigmaH), color = variable)
  ) +
  # Mosquito thermal tolerance range lines
  geom_hline(
    data = MosqThermRange_df,
    aes(yintercept = CTmin_V0, colour = "VTTR"),
    lwd = 1.275
  ) +
  geom_hline(
    data = MosqThermRange_df,
    aes(yintercept = CTmax_V0, colour = "VTTR"),
    lwd = 1.275
  ) +
  # Curves showing CTmin and CTmax
  geom_line(
    data = filter(CTRange_df, variable == "CTmin"),
    lwd = 1
  ) +
  geom_line(
    data = filter(CTRange_df, variable == "CTmax"),
    lwd = 1
  ) +
  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(1E-2, 1E5),
    breaks = 10^seq(-1, 4),
    labels = TeX(c("$0.1$", "$1$", "$10$", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: small buffer space
  scale_y_continuous(
    name = expression("Temperature "(degree * C)),
    expand = c(0.05, 0.05),
    limits = c(min(MosqThermRange_df$CTmin_V0), max(MosqThermRange_df$CTmax_V0)),
    breaks = seq(floor(range(CTRange_df$value, na.rm = TRUE)[1]),
                 floor(range(CTRange_df$value, na.rm = TRUE)[2]),
                 by = 2)
  ) +
  # linetype:
  scale_linetype_manual(
    name = "Vertebrate host biting tolerance\n(bites per host per day)",
    values = c("solid", "dashed", "longdash", "dotted"),
    breaks = c(1, 10, 100, Inf),
    labels = unname(c("1 (Chitnis)", "10 (Chitnis)", "100 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)")))
  ) +
  # color:
  scale_colour_manual(
    name = "Thermal extrema",
    breaks = c("CTmax", "CTmin", "VTTR"),
    labels = c("Critical maximum", "Critical minimum", "Mosquito thermal\ntolerance range"),
    values = c("red", "blue", "grey"),
    guide = guide_legend(keyheight = unit(40, "cm"))
  ) +
  # faceting:
  facet_wrap(~system_label,scales = "free",nrow = 2,labeller = labeller()) +
  # legend:
  guides(
    color = guide_legend(override.aes = list(size = 4), order = 1),
    linetype = guide_legend(keywidth = 4, order = 2),
  ) +
  # theme options:
  theme_minimal_hgrid() +
  theme(
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 10,
      hjust = 0
    )
  )

@@

plot.R0.rel.sens <- R0.HPD %>%
  filter(KH %in% c(1) & sigmaH %in% c(100, Inf)) %>%
  # filter(!(KH == 100 & sigmaH == Inf)) %>%
  filter(rel_HPD_width != 0) %>%
  # For each KH value, sum up all sensitivity values to get total sensitivity across parameters
  group_by(system_ID, sigmaH, KH, Temperature) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each sensitivity value by the total sensitivity
  mutate(sens_rel = rel_HPD_width / sens_total) %>%
  arrange(sens_rel) %>%
  arrange(focal_var) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = Temperature, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_continuous(
    # limits = Temp_range_for_plot,
    expand = c(0, 0)
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $R_0$ HPD width"))
  ) +
  facet_grid(
    cols = vars(system_label),
    rows = vars(KH, sigmaH),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
      KH = as_labeller(appender_KH, default = label_parsed)
    ),
    scales = "free"
  ) +
  theme_minimal() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

@@

Topt.HPD <- Topt.HPD %>%
  ungroup() %>%
  pathosystem_labeller() %>%
  filter(!is.na(rel_HPD_width)) %>%
  # For each KH value, sum up all sensitivity values to get total sensitivity
  group_by(system_ID, sigmaH, KH) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each sensitivity value by the total sensitivity
  mutate(sens_rel = rel_HPD_width / sens_total) # %>%
# arrange(sens_rel)

@@

plot.Topt.rel.sens <- Topt.HPD %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E3),
    breaks = 10^seq(-2, 4, 1),
    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $T_{opt}$ HPD width"))
  ) +
  # scale_y_continuous(
  #   limits = c(0,1)
  # ) +
  facet_wrap(~system_label, scales = "free") +
  theme_minimal() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )
shift_legend(plot.Topt.rel.sens)
```

@@

CTmin_df <- CT.HPD %>%
  filter(variable == "CTmin") %>%
  filter(sigmaH %in% c(10, Inf)) %>%
  filter(!is.na(rel_HPD_width)) %>%
  # For each KH value, sum up all sensitivity values to get total sensitivity
  group_by(system_ID, sigmaH, KH) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each sensitivity value by the total sensitivity
  mutate(sens_rel = rel_HPD_width / sens_total) #%>%

  # Make a stacked plot, colored by parameter
plot.CTmin.rel.sens <- CTmin_df %>% 
  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    breaks = 10^seq(-2, 4, 1),
    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $CT_{min}$ HPD width"))
  ) +
  facet_grid(
    cols = vars(system_label),
    rows = vars(sigmaH),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed)
    ),
    scales = "free"
  ) +
  theme_minimal() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    ),
    panel.spacing.x = unit(2, "lines")
  )
plot.CTmin.rel.sens
```

@@

plot.CTmax.rel.sens <- CT.HPD %>%
  filter(variable == "CTmax") %>%
  filter(sigmaH %in% c(10, Inf)) %>%
  filter(!is.na(rel_HPD_width)) %>%
  # For each KH value, sum up all sensitivity values to get total sensitivity
  group_by(system_ID, sigmaH, KH) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each sensitivity value by the total sensitivity
  mutate(sens_rel = rel_HPD_width / sens_total) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    breaks = 10^seq(-2, 4, 1),
    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $CT_{max}$ HPD width"))
  ) +
  facet_grid(
    cols = vars(system_label),
    rows = vars(sigmaH),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed)
    ),
    scales = "free"
  ) +
  theme_minimal() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    ),
    panel.spacing.x = unit(2, "lines")
  )
plot.CTmax.rel.sens
```

@@

plot.CTwidth.rel.sens <- CT.HPD %>%
  filter(variable == "CTwidth") %>%
  filter(sigmaH %in% c(10, Inf)) %>%
  filter(!is.na(rel_HPD_width)) %>%
  # For each KH value, sum up all sensitivity values to get total sensitivity
  group_by(system_ID, sigmaH, KH) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each sensitivity value by the total sensitiviWty
  mutate(sens_rel = rel_HPD_width / sens_total) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    breaks = 10^seq(-2, 4, 1),
    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $CT_{width}$ HPD width"))
  ) +
  facet_grid(
    cols = vars(system_label),
    rows = vars(sigmaH),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed)
    ),
    scales = "free"
  ) +
  theme_minimal() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    ),
    panel.spacing.x = unit(2, "lines")
  )
plot.CTwidth.rel.sens
```

>>>>

# Label functions:
appender_sigmaH <- function(string) {
  ifelse(string == "Inf", 
         unname(TeX(paste("$\\sigma_H = \\infty$"))),
         unname(TeX(paste("$\\sigma_H = $", string))))
}
appender_KH <- function(string) {
  unname(TeX(paste("$K_H = $", string)))
}

@@

## PLOT ##
R0_plot <- R0_df %>%
  ggplot(mapping = aes(x = sigmaH_proxy, y = Temperature)) +
  # Mosquito thermal tolerance range lines
  geom_hline(
    data = MosqThermRange_df,
    aes(yintercept = CTmin_V0, colour = "VTTR"),
    lwd = 1.275
  ) +
  geom_hline(
    data = MosqThermRange_df,
    aes(yintercept = CTmax_V0, colour = "VTTR"),
    lwd = 1.275
  ) +
  # R0 contours for FINITE sigmaH:
  geom_contour_filled(
    data = filter(R0_df, sigmaH_proxy < infinite_divide**0.98),
    mapping = aes(z = R0),
    breaks = fill_breaks
  ) +
  # R0 contours for INFINITE sigmaH:
  geom_contour_filled(
    data = filter(R0_df, sigmaH_proxy > infinite_divide**1.02),
    mapping = aes(z = R0),
    breaks = fill_breaks
  ) +
  # R0 = 1 contour:
  geom_contour(aes(colour = "R0=1", z = R0), breaks = c(1), size = 1) +
  # Topt curve:
  geom_path(
    data = filter(Topt_for_R0_df, KH %in% c(.1, 1, 10)) %>% arrange(sigmaH_proxy),
    mapping = aes(
      x = sigmaH_proxy,
      y = median,
      colour = "Topt"
    ),
    lwd = 1,
    linetype = 1
  ) +
  # white lines breaking up finite/infinite sigmaH values
  geom_vline(
    aes(xintercept = 0.85 * infinite_divide),
    colour = "white",
    lwd = .8,
    show.legend = FALSE
  ) +
  geom_vline(
    aes(xintercept = infinite_divide),
    colour = "white",
    lwd = .8,
    show.legend = FALSE
  ) +
  geom_vline(
    aes(xintercept = 1.2 * infinite_divide),
    colour = "white",
    lwd = .8,
    show.legend = FALSE
  ) +
  # x-axis:
  scale_x_log10(
    name = TeX("Vertebrate host biting tolerance (bites per host per day)"),
    breaks = sigmaH_breaks_heatmap,
    labels = sigmaH_labels_heatmap,
    expand = c(0, 0)
  ) +
  # y-axis:
  scale_y_continuous(
    name = expression("Temperature "(degree * C)),
    expand = c(0, 0),
    limits = c(16, 35),
    breaks = seq(10, 36, by = 2)
  ) +
  # color:
  scale_colour_manual(
    name = "",
    labels = c(
      "R0=1" = unname(TeX("$R_0=1$")),
      "Topt" = "Transmission\nthermal\noptimum",
      "VTTR" = "Mosquito\npopulation\nthermal\nniche"
    ),
    values = c("black", "purple", "grey"),
    guide = guide_legend(
      order = 1,
      keyheight = unit(2, "cm"),
      override.aes = list(size = 6)
    )
  ) +
  # fill:
  scale_fill_manual(
    name = TeX("$R_0$"),
    values = my.cols,
    guide = guide_colorsteps(
      order = 2,
      breaks = fill_breaks,
      barheight = unit(8, "cm")
    )
  ) +
  # faceting:
  facet_grid(
    rows = vars(KH),
    cols = vars(system_label),
    labeller = labeller(.rows = mylabels,
                        .cols = R0_heatmap_labels),
    # repeat.tick.labels = "left"
  ) +
  # theme options:
  theme_minimal_hgrid(11) +
  theme(
    axis.line = element_line(),
    legend.text = element_text(size = 10),
    legend.text.align = 0,
    strip.text.y = ggtext::element_markdown(
      size = 7,
      hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 7,
      hjust = 0),
    panel.spacing = unit(2, "pt")
    )

@@

CTRange_plots <- CTRange_df %>%
  ## Set up plot ##
  # x-axis = population density, y-axis = temperature,
  # color = thermal extrema, linetype = sigmaH
  ggplot(
    aes(x = KH, y = value, linetype = as.factor(sigmaH), color = variable)
  ) +
  # Mosquito thermal tolerance range lines
  geom_hline(
    data = MosqThermRange_df,
    aes(yintercept = CTmin_V0, colour = "VTTR"),
    lwd = 1.275
  ) +
  geom_hline(
    data = MosqThermRange_df,
    aes(yintercept = CTmax_V0, colour = "VTTR"),
    lwd = 1.275
  ) +
  # Curves showing CTmin and CTmax
  geom_line(
    data = filter(CTRange_df, variable == "CTmin"),
    lwd = 1
  ) +
  geom_line(
    data = filter(CTRange_df, variable == "CTmax"),
    lwd = 1
  ) +
  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(1E-2, 1E5),
    breaks = 10^seq(-1, 4),
    labels = TeX(c("$0.1$", "$1$", "$10$", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: small buffer space
  scale_y_continuous(
    name = expression("Temperature "(degree * C)),
    expand = c(0.05, 0.05),
    limits = c(min(MosqThermRange_df$CTmin_V0), max(MosqThermRange_df$CTmax_V0)),
    breaks = seq(floor(range(CTRange_df$value, na.rm = TRUE)[1]),
                 floor(range(CTRange_df$value, na.rm = TRUE)[2]),
                 by = 2)
  ) +
  # linetype:
  scale_linetype_manual(
    name = "Vertebrate host biting tolerance\n(bites per host per day)",
    values = c("solid", "dashed", "longdash", "dotted"),
    breaks = c(1, 10, 100, Inf),
    labels = unname(c("1 (Chitnis)", "10 (Chitnis)", "100 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)")))
  ) +
  # color:
  scale_colour_manual(
    name = "Thermal extrema",
    breaks = c("CTmax", "CTmin", "VTTR"),
    labels = c("Critical maximum", "Critical minimum", "Mosquito population\nthermal niche"),
    values = c("red", "blue", "grey"),
    guide = guide_legend(keyheight = unit(40, "cm"))
  ) +
  # faceting:
  facet_wrap(~system_label,scales = "free",nrow = 2,labeller = labeller()) +
  # legend:
  guides(
    color = guide_legend(override.aes = list(size = 4), order = 1),
    linetype = guide_legend(keywidth = 4, order = 2),
  ) +
  # theme options:
  theme_minimal_hgrid() +
  theme(
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 10,
      hjust = 0
    )
  )

@@

plot.R0.rel.sens <- R0.HPD %>%
  filter(KH %in% c(1) & sigmaH %in% c(100, Inf)) %>%
  # filter(!(KH == 100 & sigmaH == Inf)) %>%
  filter(rel_HPD_width != 0) %>%
  # For each KH value, sum up all sensitivity values to get total sensitivity across parameters
  group_by(system_ID, sigmaH, KH, Temperature) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each sensitivity value by the total sensitivity
  mutate(sens_rel = rel_HPD_width / sens_total) %>%
  arrange(sens_rel) %>%
  arrange(focal_var) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = Temperature, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_continuous(
    # limits = Temp_range_for_plot,
    expand = c(0, 0)
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $R_0$ HPD width"))
  ) +
  facet_grid(
    cols = vars(system_label),
    rows = vars(KH, sigmaH),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed)
    ),
    scales = "free"
  ) +
  theme_minimal() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

@@

Topt.HPD <- Topt.HPD %>%
  ungroup() %>%
  distinct() %>% 
  filter(!is.na(HPD_width)) %>% 
  pathosystem_labeller() %>%
  filter(!is.na(rel_HPD_width)) %>%
  # For each KH value, sum up all sensitivity values to get total sensitivity
  group_by(system_ID, sigmaH, KH) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each sensitivity value by the total sensitivity
  mutate(sens_rel = rel_HPD_width / sens_total) # %>%
# arrange(sens_rel)

@@

plot.Topt.rel.sens <- Topt.HPD %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E3),
    breaks = 10^seq(-2, 4, 1),
    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $T_{opt}$ HPD width"))
  ) +
  # scale_y_continuous(
  #   limits = c(0,1)
  # ) +
  facet_wrap(~system_label) +
  theme_minimal() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )
shift_legend(plot.Topt.rel.sens)
```

@@

CTmin_df <- CT.HPD %>%
  filter(variable == "CTmin") %>%
  filter(sigmaH %in% c(100, Inf)) %>%
  filter(!is.na(rel_HPD_width)) %>%
  # For each KH value, sum up all sensitivity values to get total sensitivity
  group_by(system_ID, sigmaH, KH) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each sensitivity value by the total sensitivity
  mutate(sens_rel = rel_HPD_width / sens_total) #%>%

  # Make a stacked plot, colored by parameter
plot.CTmin.rel.sens <- CTmin_df %>% 
  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    breaks = 10^seq(-2, 4, 1),
    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $CT_{min}$ HPD width"))
  ) +
  facet_grid(
    cols = vars(system_label),
    rows = vars(sigmaH),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed)
    )
  ) +
  theme_minimal() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 8,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    ),
    panel.spacing.x = unit(2, "lines")
  )
plot.CTmin.rel.sens
```

@@

plot.CTmax.rel.sens <- CT.HPD %>%
  filter(variable == "CTmax") %>%
  filter(sigmaH %in% c(100, Inf)) %>%
  filter(!is.na(rel_HPD_width)) %>%
  # For each KH value, sum up all sensitivity values to get total sensitivity
  group_by(system_ID, sigmaH, KH) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each sensitivity value by the total sensitivity
  mutate(sens_rel = rel_HPD_width / sens_total) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    breaks = 10^seq(-2, 4, 1),
    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $CT_{max}$ HPD width"))
  ) +
  facet_grid(
    cols = vars(system_label),
    rows = vars(sigmaH),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed)
    )
  ) +
  theme_minimal() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 8,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    ),
    panel.spacing.x = unit(2, "lines")
  )
plot.CTmax.rel.sens
```

@@

plot.CTwidth.rel.sens <- CT.HPD %>%
  filter(variable == "CTwidth") %>%
  filter(sigmaH %in% c(100, Inf)) %>%
  filter(!is.na(rel_HPD_width)) %>%
  # For each KH value, sum up all sensitivity values to get total sensitivity
  group_by(system_ID, sigmaH, KH) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each sensitivity value by the total sensitiviWty
  mutate(sens_rel = rel_HPD_width / sens_total) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    breaks = 10^seq(-2, 4, 1),
    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $CT_{width}$ HPD width"))
  ) +
  facet_grid(
    cols = vars(system_label),
    rows = vars(sigmaH),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(
        appender_sigmaH, default = label_parsed)
    )
  ) +
  theme_minimal() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 8,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    ),
    panel.spacing.x = unit(2, "lines")
  )
plot.CTwidth.rel.sens
```
